|

### 2021-03-14 appendix/appendix.Rmd
tidy binomial tests and add todo to appendix

# Required packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "devtools", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux2
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux2
```

>>>>

# Required packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "devtools", "data.table",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick",
          'stargazer', 'pander', 'broom')

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "N")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2 == "logN")
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```

@@

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- filter(dat, indepvar2=='K')
aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
```
